Bricking up backdoors in Intrusion Detection Systems

### 2019-09-10 ex2/paper/paper.tex
Make title fit in one line
Make caption shorter

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Bricking up and overgrowing backdoors in Intrusion Detection Systems}

@@

\autoref{fig:pruningExample} shows an example of variant (3) of pruning applied to a tree
\begin{figure}[h]
\includegraphics[width=\columnwidth]{../prune_CAIA_backdoor_15/prune_oh_d.pdf}
\caption{Performance metrics throughout the pruning process for \unsw{}. Considering only harmless leaves and pruning leaves with smaller depth first. The longer the dashes, the higher the fraction of the validation set being used (from 0.01 until 1).}
\label{fig:performancePruningRF}
\end{figure}
%\todo{Max: Which pruning algorithm actually?}
and \autoref{fig:performancePruningRF} shows the resulting accuracy for pruning according to variant (3) for the \unsw{} dataset. With sufficient neurons being pruned, the accuracy of the backdoor approaches zero. The accuracy for the regular data does not decrease; it even increases by
%thanks to the the pruning also
reducing overfitting. %With a significantly smaller validation set, pruning takes longer to remove the backdoor
%until it works
%but it still works. This is an important finding as a large validation dataset makes it hard for users without access to expensive hardware to perform the pruning. 
Also with only a very small validation dataset, the pruning still works as expected. For \cic{} we get similar results, but the pruning does not remove the backdoor completely (\~30\% backdoor accuracy remains). We attribute this to the fact, that in this dataset there are also regular flows which have $\text{stddev}(\text{TTL}) > 0$. And thus backdoored flows cannot always be sharply distinguished from regular flows. We find that pruning only harmless leaves is very beneficial for \unsw{} but not for \cic{}. However, considering depth when making the decision which leaf to prune first leads to the backdoor being removed considerably earlier in the pruning process.

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Bricking up backdoors in Intrusion Detection Systems}

@@

\autoref{fig:pruningExample} shows an example of variant (3) of pruning applied to a tree
\begin{figure}[h]
\includegraphics[width=\columnwidth]{../prune_CAIA_backdoor_15/prune_oh_d.pdf}
\caption{Performance metrics throughout the pruning process for \unsw{}. Considering only harmless leaves and depth. Dash length proportional to validtion set size (from 0.01 until 1).}
\label{fig:performancePruningRF}
\end{figure}
%\todo{Max: Which pruning algorithm actually?}
and \autoref{fig:performancePruningRF} shows the resulting accuracy for pruning according to variant (3) for the \unsw{} dataset. With sufficient neurons being pruned, the accuracy of the backdoor approaches zero. The accuracy for the regular data does not decrease; it even increases by
%thanks to the the pruning also
reducing overfitting. %With a significantly smaller validation set, pruning takes longer to remove the backdoor
%until it works
%but it still works. This is an important finding as a large validation dataset makes it hard for users without access to expensive hardware to perform the pruning. 
Also with only a very small validation dataset, the pruning still works as expected. For \cic{} we get similar results, but the pruning does not remove the backdoor completely (\~30\% backdoor accuracy remains). We attribute this to the fact, that in this dataset there are also regular flows which have $\text{stddev}(\text{TTL}) > 0$. And thus backdoored flows cannot always be sharply distinguished from regular flows. We find that pruning only harmless leaves is very beneficial for \unsw{} but not for \cic{}. However, considering depth when making the decision which leaf to prune first leads to the backdoor being removed considerably earlier in the pruning process.
